flowCore: A Bioconductor software package for high throughput flow cytometry analysis

### 2008-08-12 paper/manuscript.tex
tidying up the abstract a bit
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@33198 bc3139a8-67e5-0310-9ffc-ced21a209358

\section*{Abstract}
\subsubsection*{Background}
Recent advances in automation technologies have enabled the use of
flow-cytometry high content screening (FH-HCS). However, data
management and data analysis methods have not advanced sufficiently
far from the inital small-scale studies to support the large complex
data sets generated in FH-HCS applications.
\subsubsection*{Methods}
In this manuscript, we present \Rpackage{flowCore} a set of flexible
and well structured computational tools for FC-HCS data analysis based
on the open source statistical software R in conjunction with the
Bioconductor Project.
\subsubsection*{Results}
Through \Rpackage{flowCore}, we provide the FCM community a shared
research platform that enables bioinformaticians, computer scientists,
and statisticians to work collaboratively with biologists and
clinicians to develop novel methods for FCM data analysis.
\subsubsection*{Conclusions}
We hope that our framework will be the foundation for fruitful shared
research by many collaborators from multiple scientific fields and
will help resolve bottlenecks that currently prevent the further
development of and deployment of FC-HCS to increasingly complex and
important scientific and clinical applications.

>>>>

\section*{Abstract}
\subsubsection*{Background}
Recent advances in automation technologies have enabled the use of
flow-cytometry high content screening (FH-HCS). However, data
management and data analysis methods have not advanced sufficiently
far from the inital small-scale studies to support the large complex
data sets generated in FH-HCS applications.
\subsubsection*{Methods}
In this manuscript, we describe a set of flexible
computational tools for FC-HCS data analysis written 
in R and freely available from the Bioconductor Project.

\subsubsection*{Results}
The \Rpackage{flowCore} package provides the FCM community a shared
research platform that enables bioinformaticians, computer scientists,
and statisticians to work collaboratively with biologists and
clinicians to develop novel methods for FCM data analysis.
\subsubsection*{Conclusions}
We hope that our framework will be the foundation for fruitful 
collaborative research involving multiple scientific fields and
that it will help facilitate the
development and deployment of FC-HCS methods to complex 
scientific and clinical applications.
